Large and Infinitary Quotient Inductive-Inductive Types

### 2019-12-31 draft/paper.tex
paper

\newcommand{\bCon}{\boldsymbol{\Con}}
\newcommand{\bTy}{\boldsymbol{\Ty}}
\newcommand{\bSub}{\boldsymbol{\Sub}}
\newcommand{\bTm}{\boldsymbol{\Tm}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\bDelta}{\boldsymbol{\Delta}}
\newcommand{\bsigma}{\boldsymbol{\sigma}}
\newcommand{\bdelta}{\boldsymbol{\delta}}
\newcommand{\bepsilon}{\boldsymbol{\epsilon}}
\newcommand{\bt}{\boldsymbol{t}}
\newcommand{\bu}{\boldsymbol{u}}
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\ba}{\boldsymbol{a}}
\newcommand{\bB}{\boldsymbol{B}}
\newcommand{\bid}{\boldsymbol{\id}}
\newcommand{\bemptycon}{\boldsymbol{\emptycon}}
\newcommand{\bSet}{\boldsymbol{\Set}}
\newcommand{\bU}{\boldsymbol{\U}}
\newcommand{\bEl}{\boldsymbol{\El}}
\newcommand{\bPii}{\boldsymbol{\Pi}}
\newcommand{\bappi}{\boldsymbol{\mathsf{app}}}
\newcommand{\blami}{\boldsymbol{\mathsf{lam}}}

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ulGamma}{\ul{\Gamma}}
\newcommand{\ulDelta}{\ul{\Delta}}
\newcommand{\ulsigma}{\ul{\sigma}}
\newcommand{\uldelta}{\ul{\delta}}
\newcommand{\ulepsilon}{\ul{\epsilon}}
\newcommand{\ult}{\ul{t}}
\newcommand{\ulu}{\ul{u}}
\newcommand{\ulA}{\ul{A}}
\newcommand{\ulB}{\ul{B}}

@@

In the following examples, we leave the abstracted $M : \ToS_{0,j}$ implicit.

@@

We make a similar choice in the interpretation of signatures themselves: we use
structured CwFs instead of lex categories to model notions of induction. The
reason here is that CwFs allow us to compute induction principles in strictly
the same way as one would write them down in type theory, since we have $\Ty$
and $\Tm$ for a primitive notion of dependent objects and morphisms. In
contrast, dependent objects in lex categories is a derived notion, and the
induction principles we get are only up to isomorphism. This issue is perhaps
not relevant from a purely categorical perspective, but we are concerned with
eventually implementing QIITs in proof assistants, so we prefer if our semantics
computes strictly.

In the following, we fix $i$ and $j$ levels, and define a model $M : \ToS_{i,
  1+\max(i,j+1)}$, such than $\Con_M$ is a type of structured categories (of
algebras). The level $i$ marks the level of all external sets in function
domains, and $j$ marks the level of all internal sorts in an algebra. Hence,
every algebra has level $\max(i,j+1)$. The bump is only needed for $j$, since
algebras only contain elements of $T : \Set_j$ types, while inductive sets are
themselves elements of $\Set_i$. For example, $NatAlg_i : \Set_{\max(0, i+1)}$.

@@

We define $\bCon : \Set_{1+\max(i,j+1)}$ as $\flCwF_{\max(i,j+1)}$.
%% We define
%% $\flCwF$ as follows.

\begin{definition}[Finite limit CwFs]\label{def:flCwF}
For a level $i$, there is a cETT type $\flCwF_i : \Set_{i+1}$, which is an
iterated $\Sigma$-type with the following components:
\begin{enumerate}
  \item A CwF with underlying sets all in $\Set_i$. We reuse the component
    notations from Definition \ref{def:tos}.
  \item $\Sigma$-type $\Sg : (A : \Ty\,\Gamma)\ra \Ty\,(\Gamma \ext A)
    \ra \Ty\,\Gamma$, with term formers $\proj1$, $\proj2$ and $\blank,\blank$.
  \item Identity type $\Id : (A : \Ty\,\Gamma)\ra \Tm\,\Gamma\,A\ra
    \Tm\,\Gamma\,A\ra \Ty\,\Gamma$, with $\refl$, equality reflection and UIP.
  \item Constant families. This includes a type former $\Kfam : \Con \ra
    \Ty\,\Gamma$, where $\Gamma$ is implicitly quantified, together with $\lamK
    : \Sub\,\Gamma\,\Delta \ra \Tm\,\Gamma\,(\Kfam\,\Delta)$ and its inverse
    $\appK$. The idea is that $\Kfam\,\Delta$ is a representation of $\Delta$ as
    a type in any context. Clairambault and Dybjer called constant families
    ``democracy'' in \cite{clairambault2014biequivalence}.
\end{enumerate}
\end{definition}

@@

\begin{definition} A \emph{vertical morphism} lies over an identity morphism. We use this definition for context and type morphisms as well.
\end{definition}

@@

\begin{definition}[Context iso-cleaving] This lifts a base context isomorphism to a displayed one. It consists of
\begin{alignat*}{3}
  & \coe &&: \ulGamma \simeq \ulDelta \ra \Con_{\bA}\,\ulGamma \ra \Con_{\bA}\,\ulDelta\\
  & \coh &&: (\ulsigma : \ulGamma \simeq \ulDelta)(\Gamma : \Con_{\bA}\,\ulGamma)
           \ra \Gamma \simeq_{\ulsigma} \coe\,\ulsigma\,\Gamma\\
  & \coe_{\id} && : \coe\,\id\,\Gamma = \Gamma\\
  & \coe_{\circ} && : \coe\,(\ulsigma\circ\uldelta)\,\Gamma = \coe\,\ulsigma\,(\coe\,\uldelta\,\Gamma)\\
  & \coh_{\id} && : \coh\,\id\,\Gamma = \id\\
  & \coh_{\circ} && : \coh\,(\ulsigma\circ\uldelta)\,\Gamma = \coh\,\ulsigma\,(\coe\,\uldelta\,\Gamma)
          \circ \coh\,\uldelta\,\Gamma
\end{alignat*}
Here, $\coe$ and $\coh$ abbreviate ``coercion'' and ``coherence'' respectively.
\end{definition}

\begin{definition}[Type iso-cleaving] This consists of
\begin{alignat*}{3}
  & \coe &&: \ulA \simeq \ulB \ra \Ty_{\bA}\,\Gamma\,\ulA \ra \Ty_{\bA}\,\Gamma\,\ulB\\
  & \coh &&: (\ult : \ulA \simeq \ulB)(A : \Ty_{\bA}\,\Gamma\,\ulA)
           \ra A \simeq_{\ult} \coe\,\ult\,A\\
  & \coe_{\id} && : \coe\,\id\,A = A\\
  & \coe_{\circ} && : \coe\,\ult\,(\coe\,\uldelta\,A) = \coe\,(\ult\circ\uldelta)\,A\\
  & \coh_{\id} &&: \coh\,\id\,A = \id\\
  & \coh_{\circ} &&: \coh\,(\ult\circ\uldelta)\,A = \coh\,\ult\,(\coe\,\uldelta\,A)
          \circ \coh\,\uldelta\,A
\end{alignat*}
Additionally, for $\sigma : \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma$, we have
\begin{alignat*}{3}
  & \coe_{[]} &&: \coe\,(\ult[\ulsigma])\,(A[\sigma]) = (\coe\,\ult\,A)[\sigma]\\
  & \coh_{[]} &&: \coh\,(\ult[\ulsigma\circ \p,\q])\,(A[\sigma]) = (\coh\,\ult\,A)[\sigma]
\end{alignat*}

@@

@@

\begin{definition} $\boldsymbol{\Tm\,\Gamma\,A} : \Set_{1 + \max(i, j)}$ is defined as the type of
\emph{weak flCwF sections} of $\bA$. The underlying functions of $\bt :
\bTm\,\bGamma\,\bA$ are as follows:
\begin{alignat*}{3}
  & \bt : (\ulGamma : \Con_{\bGamma}) \ra \Con_{\bA}\,\ulGamma\\
  & \bt : (\ulsigma : \Sub_{\bGamma}\,\ulGamma\,\ulDelta)
         \ra \Sub_{\bA}\,(\bt\,\ulGamma)\,(\bt\,\ulDelta)\,\ulsigma\\
  & \bt : (\ulA : \Ty_{\bGamma}) \ra \Ty_{\bA}\,(\bt\,\ulGamma)\,\ulA\\
  & \bt : (\ult : \Tm_{\bGamma}\,\ulGamma\,\ulA) \ra
          \Tm_{\bA}\,(\bt\,\ulGamma)\,(\bt\,\ulA)\,\ult
\end{alignat*}
Such that
\begin{enumerate}
  \item $\bt\,(\ulA[\ulsigma]) = (\bt\,\ulA)\,[\bt\,\ulsigma]$
  \item $\bt\,(\ult[\ulsigma]) = (\bt\,\ult)\,[\bt\,\ulsigma]$
  \item The unique map $\epsilon_{\bA} : \Sub\,(\bt\,\emptycon)\,\emptycon\,\id$ has a vertical retraction.
  \item Each $(\bt\,\p,\,\bt\,\q) : \Sub\,(\bt\,(\ulGamma\,\ext\,\ulA))\,(\bt\,\ulGamma\,\ext\,\bt\,\ulA)\,\id$ has a vertical inverse.
\end{enumerate}
\end{definition}
Similarly to Definition \ref{def:weakmorphism}, we denote the evident preservation
isomorphisms as $\bt_{\emptycon} : \bt\,\emptycon \simeq_{\id} \emptycon$ and
$\bt_{\ext} : \bt\,(\ulGamma\ext \ulA) \simeq_{\id} \bt\,\ulGamma \ext
\bt\,\ulA$. In short, weak section is a dependently typed analogue of weak
morphism, with dependent underlying functions and displayed preservation
isomorphisms. We also have the derived fl-preservation isomorphisms.

@@

\begin{definition}
We define $\boldsymbol{\El : \Tm\,\Gamma\,\U \ra \Ty\,\Gamma}$ as discrete
isofibration formation. For $\boldsymbol{a : \Tm\,\Gamma\,\U}$, the underlying
sets of $\bEl\,\ba$ are the following:
\begin{alignat*}{3}
  & \Con_{\bEl\,\ba}\,\ulGamma && :\equiv \ba\,\ulGamma\\
  & \Sub_{\bEl\,\ba}\,\Gamma\,\Delta\,\ulsigma && :\equiv \ba\,\ulsigma\,\Gamma = \Delta\\
  & \Ty_{\bEl\,\ba}\,\Gamma\,\ulA && :\equiv \ba\,\ulA\,\Gamma\\
  & \Tm_{\bEl\,\ba}\,\Gamma\,A\,\ult && :\equiv \ba\,\ult\,\Gamma = A
\end{alignat*}
Hence, in $\bEl\,\ba$, $\Sub$ and $\Tm$ are propositional. We use the
isomorphisms $\ba_{\emptycon} : \ba\,\emptycon \simeq \top$ and $\ba_{\ext} :
\ba\,(\ulGamma\ext\ulA) \simeq (\Gamma :
\ba\,\ulGamma)\times(\ba\,\ulA\,\Gamma)$ to define empty context and context
extension:
\begin{alignat*}{3}
  & \emptycon_{\bEl\,\ba} && :\equiv \ba_{\emptycon}^{-1}\,\tt\\
  & (\Gamma\ext_{\bEl\,\ba} A) && :\equiv \ba_{\ext}^{-1}\,(\Gamma,\,A)
\end{alignat*}
We likewise use preservation isomorphisms to define $\K$, $\Id$ and $\Sigma$.
Context coercion is $\coe\,\ulsigma\,\Gamma :\equiv \ba\,\ulsigma\,\Gamma$. Type coercion, for $A : \ba\,\ulA\,\Gamma$ is given as $\coe\,\ult\,A :\equiv \ba\,\ult\,(\ba_{\ext}^{-1}\,(\Gamma,\,A))$.
\end{definition}

@@

For $\boldsymbol{a : \Tm\,\Gamma\,\U}$ and $\boldsymbol{B :
  \Ty\,(\Gamma\ext\El\,a)}$, we aim to define $\boldsymbol{\Pi\,a\,B}
\boldsymbol{:} \bTy\,\bGamma$. We define this as a dependent product of
isofibrations, indexed by a discrete domain. $\bPii$ would not be definable with
general $\bA \boldsymbol{:} \bTy\,\bGamma$ domain, since variance issues already
prevent $\Pi$-types in the CwF of categories, see e.g. \cite{TODO}.

>>>>

\newcommand{\bCon}{\boldsymbol{\Con}}
\newcommand{\bTy}{\boldsymbol{\Ty}}
\newcommand{\bSub}{\boldsymbol{\Sub}}
\newcommand{\bTm}{\boldsymbol{\Tm}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\bDelta}{\boldsymbol{\Delta}}
\newcommand{\bsigma}{\boldsymbol{\sigma}}
\newcommand{\bdelta}{\boldsymbol{\delta}}
\newcommand{\bepsilon}{\boldsymbol{\epsilon}}
\newcommand{\bt}{\boldsymbol{t}}
\newcommand{\bu}{\boldsymbol{u}}
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\ba}{\boldsymbol{a}}
\newcommand{\bb}{\boldsymbol{b}}
\newcommand{\bB}{\boldsymbol{B}}
\newcommand{\bid}{\boldsymbol{\id}}
\newcommand{\bemptycon}{\boldsymbol{\emptycon}}
\newcommand{\bSet}{\boldsymbol{\Set}}
\newcommand{\bU}{\boldsymbol{\U}}
\newcommand{\bEl}{\boldsymbol{\El}}
\newcommand{\bPii}{\boldsymbol{\Pi}}
\newcommand{\bPie}{\boldsymbol{\Pie}}
\newcommand{\bPiinf}{\boldsymbol{\Piinf}}
\newcommand{\bappi}{\boldsymbol{\mathsf{app}}}
\newcommand{\blami}{\boldsymbol{\mathsf{lam}}}

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ulGamma}{\ul{\Gamma}}
\newcommand{\ulDelta}{\ul{\Delta}}
\newcommand{\ulgamma}{\ul{\gamma}}
\newcommand{\uldelta}{\ul{\delta}}
\newcommand{\ulsigma}{\ul{\sigma}}
\newcommand{\ulepsilon}{\ul{\epsilon}}
\newcommand{\ult}{\ul{t}}
\newcommand{\ulu}{\ul{u}}
\newcommand{\ulA}{\ul{A}}
\newcommand{\ulB}{\ul{B}}

@@

In the following examples, we leave the abstracted $M : \ToS_{i,j}$ implicit.

@@

We make a similar choice in the interpretation of signatures themselves: we use
structured CwFs instead of lex categories. The reason here is that CwFs allow us
to compute induction principles in strictly the same way as one would write them
down in type theory, since we have $\Ty$ and $\Tm$ for a primitive notion of
dependent objects and morphisms. In contrast, dependent objects in lex
categories is a derived notion, and the induction principles we get are only up
to isomorphism. This issue is perhaps not relevant from a purely categorical
perspective, but we are concerned with eventually implementing QIITs in proof
assistants, so we prefer if our semantics computes strictly.

In the following, we fix $i$ and $j$ levels, and define a model $M : \ToS_{i,
  1+\max(i,1+j)}$, such than $\Con_M$ is a type of structured categories (of
algebras). The level $i$ marks the level of all external sets in function
domains, and $j$ marks the level of all internal sorts in an algebra. Hence,
every algebra has level $\max(i,1+j)$. The bump is only needed for $j$, since
algebras only contain elements of $T : \Set_j$ types, while inductive sets are
themselves elements of $\Set_i$. For example, $NatAlg_i : \Set_{\max(0, 1+i)}$.

@@

We define $\bCon : \Set_{1+\max(i,1+j)}$ as $\flCwF_{\max(i,1+j)}$.
%% We define
%% $\flCwF$ as follows.

\begin{definition}[Finite limit CwFs]\label{def:flCwF}
For a level $i$, there is a cETT type $\flCwF_i : \Set_{1+i}$, which is an
iterated $\Sigma$-type with the following components:
\begin{enumerate}
  \item A CwF with underlying sets all in $\Set_i$. We reuse the component
    notations from Definition \ref{def:tos}.
  \item $\Sigma$-type $\Sg : (A : \Ty\,\Gamma)\ra \Ty\,(\Gamma \ext A)
    \ra \Ty\,\Gamma$, with term formers $\proj1$, $\proj2$ and $\blank,\blank$.
  \item Identity type $\Id : (A : \Ty\,\Gamma)\ra \Tm\,\Gamma\,A\ra
    \Tm\,\Gamma\,A\ra \Ty\,\Gamma$, with $\refl$, equality reflection and UIP.
  \item Constant families. This includes a type former $\Kfam : \Con \ra
    \Ty\,\Gamma$, where $\Gamma$ is implicitly quantified, together with $\lamK
    : \Sub\,\Gamma\,\Delta \ra \Tm\,\Gamma\,(\Kfam\,\Delta)$ and its inverse
    $\appK$. The idea is that $\Kfam\,\Delta$ is a representation of $\Delta$ as
    a type in any context. Clairambault and Dybjer called constant families
    ``democracy'' in \cite{clairambault2014biequivalence}.
\end{enumerate}
\end{definition}

@@

\begin{definition} A \emph{vertical morphism} lies over an identity morphism. We use this definition for context morphisms (substitutions) and type morphisms as well.
\end{definition}

@@

\begin{definition}[Context iso-cleaving] This lifts a base context isomorphism to a displayed one. It consists of
\begin{alignat*}{3}
  & \coe &&: \ulGamma \simeq \ulDelta \ra \Con_{\bA}\,\ulGamma \ra \Con_{\bA}\,\ulDelta\\
  & \coh &&: (\ulsigma : \ulGamma \simeq \ulDelta)(\Gamma : \Con_{\bA}\,\ulGamma)
           \ra \Gamma \simeq_{\ulsigma} \coe\,\ulsigma\,\Gamma\\
  & \coe^{\id} && : \coe\,\id\,\Gamma = \Gamma\\
  & \coe^{\circ} && : \coe\,(\ulsigma\circ\uldelta)\,\Gamma = \coe\,\ulsigma\,(\coe\,\uldelta\,\Gamma)\\
  & \coh^{\id} && : \coh\,\id\,\Gamma = \id\\
  & \coh^{\circ} && : \coh\,(\ulsigma\circ\uldelta)\,\Gamma = \coh\,\ulsigma\,(\coe\,\uldelta\,\Gamma)
          \circ \coh\,\uldelta\,\Gamma
\end{alignat*}
Here, $\coe$ and $\coh$ abbreviate ``coercion'' and ``coherence'' respectively.
\end{definition}

\begin{definition}[Type iso-cleaving] This consists of
\begin{alignat*}{3}
  & \coe &&: \ulA \simeq \ulB \ra \Ty_{\bA}\,\Gamma\,\ulA \ra \Ty_{\bA}\,\Gamma\,\ulB\\
  & \coh &&: (\ult : \ulA \simeq \ulB)(A : \Ty_{\bA}\,\Gamma\,\ulA)
           \ra A \simeq_{\ult} \coe\,\ult\,A\\
  & \coe^{\id} && : \coe\,\id\,A = A\\
  & \coe^{\circ} && : \coe\,\ult\,(\coe\,\uldelta\,A) = \coe\,(\ult\circ\uldelta)\,A\\
  & \coh^{\id} &&: \coh\,\id\,A = \id\\
  & \coh^{\circ} &&: \coh\,(\ult\circ\uldelta)\,A = \coh\,\ult\,(\coe\,\uldelta\,A)
          \circ \coh\,\uldelta\,A
\end{alignat*}
Additionally, for $\sigma : \Sub_{\bA}\,\Gamma\,\Delta\,\ulsigma$, we have
\begin{alignat*}{3}
  & \coe[] &&: \coe\,(\ult[\ulsigma])\,(A[\sigma]) = (\coe\,\ult\,A)[\sigma]\\
  & \coh[] &&: \coh\,(\ult[\ulsigma\circ \p,\q])\,(A[\sigma]) = (\coh\,\ult\,A)[\sigma]
\end{alignat*}

@@

\emph{Remark.} It is not possible to model types as fibrations or opfibrations, because
we have no restriction on the variance of ToS types. For example, the type which extends
a pointed set to a $Nat$-signature is invariant in the base signature.

@@

$\boldsymbol{\Tm\,\Gamma\,A} : \Set_{1 + \max(i, 1+j)}$ is defined as the type of
\emph{weak flCwF sections} of $\bA$. The underlying functions of $\bt :
\bTm\,\bGamma\,\bA$ are as follows:
\begin{alignat*}{3}
  & \bt : (\ulGamma : \Con_{\bGamma}) \ra \Con_{\bA}\,\ulGamma\\
  & \bt : (\ulsigma : \Sub_{\bGamma}\,\ulGamma\,\ulDelta)
         \ra \Sub_{\bA}\,(\bt\,\ulGamma)\,(\bt\,\ulDelta)\,\ulsigma\\
  & \bt : (\ulA : \Ty_{\bGamma}) \ra \Ty_{\bA}\,(\bt\,\ulGamma)\,\ulA\\
  & \bt : (\ult : \Tm_{\bGamma}\,\ulGamma\,\ulA) \ra
          \Tm_{\bA}\,(\bt\,\ulGamma)\,(\bt\,\ulA)\,\ult
\end{alignat*}
Such that
\begin{enumerate}
  \item $\bt\,(\ulA[\ulsigma]) = (\bt\,\ulA)\,[\bt\,\ulsigma]$
  \item $\bt\,(\ult[\ulsigma]) = (\bt\,\ult)\,[\bt\,\ulsigma]$
  \item The unique map $\epsilon_{\bA} : \Sub\,(\bt\,\emptycon)\,\emptycon\,\id$ has a vertical retraction.
  \item Each $(\bt\,\p,\,\bt\,\q) : \Sub\,(\bt\,(\ulGamma\,\ext\,\ulA))\,(\bt\,\ulGamma\,\ext\,\bt\,\ulA)\,\id$ has a vertical inverse.
\end{enumerate}

Similarly to Definition \ref{def:weakmorphism}, we denote the evident preservation
isomorphisms as $\bt_{\emptycon} : \bt\,\emptycon \simeq_{\id} \emptycon$ and
$\bt_{\ext} : \bt\,(\ulGamma\ext \ulA) \simeq_{\id} \bt\,\ulGamma \ext
\bt\,\ulA$. In short, weak section is a dependently typed analogue of weak
morphism, with dependent underlying functions and displayed preservation
isomorphisms. We also have the derived fl-preservation isomorphisms.

@@

We define $\boldsymbol{\El : \Tm\,\Gamma\,\U \ra \Ty\,\Gamma}$ as discrete
isofibration formation. For $\boldsymbol{a : \Tm\,\Gamma\,\U}$, the underlying
sets of $\bEl\,\ba$ are the following:
\begin{alignat*}{3}
  & \Con_{\bEl\,\ba}\,\ulGamma && :\equiv \ba\,\ulGamma\\
  & \Sub_{\bEl\,\ba}\,\Gamma\,\Delta\,\ulsigma && :\equiv \ba\,\ulsigma\,\Gamma = \Delta\\
  & \Ty_{\bEl\,\ba}\,\Gamma\,\ulA && :\equiv \ba\,\ulA\,\Gamma\\
  & \Tm_{\bEl\,\ba}\,\Gamma\,A\,\ult && :\equiv \ba\,\ult\,\Gamma = A
\end{alignat*}
Hence, in $\bEl\,\ba$, $\Sub$ and $\Tm$ are propositional. We use the
isomorphisms $\ba_{\emptycon} : \ba\,\emptycon \simeq \top$ and $\ba_{\ext} :
\ba\,(\ulGamma\ext\ulA) \simeq (\Gamma :
\ba\,\ulGamma)\times(\ba\,\ulA\,\Gamma)$ to define empty context and context
extension:
\begin{alignat*}{3}
  & \emptycon_{\bEl\,\ba} && :\equiv \ba_{\emptycon}^{-1}\,\tt\\
  & (\Gamma\ext_{\bEl\,\ba} A) && :\equiv \ba_{\ext}^{-1}\,(\Gamma,\,A)
\end{alignat*}
We likewise use preservation isomorphisms to define $\K$, $\Id$ and $\Sigma$.
Context coercion is $\coe\,\ulsigma\,\Gamma :\equiv \ba\,\ulsigma\,\Gamma$. Type coercion, for $A : \ba\,\ulA\,\Gamma$ is given as $\coe\,\ult\,A :\equiv \ba\,\ult\,(\ba_{\ext}^{-1}\,(\Gamma,\,A))$.

@@

For $\boldsymbol{a : \Tm\,\Gamma\,\U}$ and $\boldsymbol{B :
  \Ty\,(\Gamma\ext\El\,a)}$, we aim to define $\boldsymbol{\Pi\,a\,B}
\boldsymbol{:} \bTy\,\bGamma$. We define this as a dependent product of
isofibrations, indexed by a discrete domain. With a general $\bA \boldsymbol{:}
\bTy\,\bGamma$ domain, $\bPii$ would not be definable, since variance issues
preclude $\Pi$-types in the CwF of categories \cite{TODO}.

%% _{(\bPii\,\ba\,\bB)}

Contexts are products of $\bB$-contexts, and types are products of $\bB$-types,
indexed respectively by contexts and types of $\bEl\,\ba$.
\begin{alignat*}{3}
  & \Con_{(\bPii\,\ba\,\bB)}\,\ulGamma &&:\equiv (\gamma : \ba\,\ulGamma)\ra \Con_{\bB}\,(\ulGamma, \gamma)\\
  & \Ty_{(\bPii\,\ba\,\bB)}\,\Gamma\,\ulA &&:\equiv (\gamma : \ba\,\ulGamma)(a : \ba\,\ulA\,\gamma)\ra \Ty_{\bB}\,(\Gamma\,\gamma)\,(\ulA, a)
\end{alignat*}
Note that since $\bB$ is over the total $\boldsymbol{(\Gamma\ext\El\,a)}$,
$\Con_{\bB}$ has a $\Sigma$-typed argument, and likewise the last argument
of every $\bB$ component.  We could define substitutions similarly, as
products of substitutions:
\begin{alignat*}{3}
  & \Sub_{(\bPii\,\ba\,\bB)}\,\Gamma\,\Delta\,\ulsigma :\equiv
  (\gamma : \ba\,\ulGamma)(\delta : \ba\,\ulDelta)
  (\sigma : \Sub_{(\bEl\,\ba)}\,\gamma\,\delta\,\ulsigma)\\
  &\hspace{6.5em}\ra \Sub_{\bB}\,(\Gamma\,\gamma)\,(\Delta\,\delta)\,(\ulsigma, \sigma)
\end{alignat*}
This would work, but we know that $\Sub_{(\bEl\,\ba)}\,\gamma\,\delta\,\ulsigma$ is defined
as $\ba\,\ulsigma\,\gamma = \delta$, so we can eliminate $\sigma$ by singleton contraction,
and use the following equivalent definition:
\begin{alignat*}{3}
  & \Sub_{(\bPii\,\ba\,\bB)}\,\Gamma\,\Delta\,\ulsigma :\equiv
  (\gamma : \ba\,\ulGamma)\ra\Sub_{\bB}\,(\Gamma\,\gamma)\,(\Delta\,(\ba\,\ulsigma\,\gamma)\,(\ulsigma, \refl)
\end{alignat*}
The benefit of the contracted definition is that it computes preservation laws
in algebra homomorphisms strictly as expected, while the non-contracted
definition computes homomorphisms as functional logical relations.

Terms are also given as a singleton-contracted version of products of terms. In
$\bPii\,\ba\,\bB$, all other structure is given pointwise by $\bB$-structure.

Iso-cleaving is given by transporting indices backwards in $\bEl\,\ba$ and outputs forwards
in $\bB$:
\begin{alignat*}{3}
  & \coe\,\ulsigma\,\Gamma &&:\equiv
    \lambda\,\gamma.\,\coe_{\bB}\,(\ulsigma,\refl)\,(\Gamma\,(\ba\,(\ulsigma^{-1})\,\gamma))\\
  & \coe\,\ult\,A &&:\equiv
    \lambda\,\gamma\,a.\,\coe_{\bB}\,(\ult,\refl)\,(A\,(\ba\,(\ult^{-1})\,(\ba_{\ext}^{-1}(\gamma,a))))
\end{alignat*}
Likewise, $\coh$-s are given by backwards-forwards $\coh$-s.

\subsection{External Function Space}

For $A : \Set_i$ and $\bB : A \ra \bTy\,\bGamma$, we define $\bPie\,A\,\bB \boldsymbol{:} \bTy\,\bGamma$ as
the evident $A$-indexed direct product of $\bB$.

\subsection{Infinitary Function Space}

For $A : \Set_i$ and $\bb : A \ra \bTm\,\bGamma\,\bU$, we aim to define
$\bPiinf\,A\,\bB \boldsymbol{:} \bTm\,\bGamma\,\bU$.
